### 2016-05-19 2016-lrec-tyvmorph/poster.tex
some fixes and stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68630 72bbbca6-d526-0410-a7d9-f06f51895060
some more hargling, but need more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68634 72bbbca6-d526-0410-a7d9-f06f51895060

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\scriptsize}
\renewcommand*{\intitlepunct}{\space}

@@

	%\headerbox{Lexicon}{name=lexicon,column=1,below=example}{
	%	%\resizebox{0.9\textwidth}{!}{
	%	%}
	%}

	\headerbox{Evaluation}{name=results,column=2,below=example}{ %lexicon}{
		%\begin{multicols}{2}	
		\htwo{5-part corpus for naïve coverage}
		%\begin{itemize}
		%	\item Naïve coverage calculated on 5-part corpus
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			 \textbf{Domain} & \textbf{Tokens} & \textbf{Coverage} (\%) \\
			\midrule
			 News       & 1,539,459 &  95.73  \\
			 Religion   & 746,124 &  93.84 \\
			 Literature & 297,830 &  91.96  \\
			 Encyclopaedic  & 276,547 & 90.86 \\
			 Folklore & 27,902 & 91.57  \\\cline{2-3}
			 Average    & -- & 92.79 \\
			\bottomrule
		\end{tabular}}
		\end{center}

		\htwo{Naïve coverage results}
		%\begin{itemize}
		%	\item Good results reflect high accuracy
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{llrr}
			\toprule
				& \textbf{count} & \textbf{precision} & \textbf{recall} \\
			\midrule
			known tokens & 1024 & 0.99 & 0.97 \\
			all tokens & 1425 & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}}
		\end{center}
		%{\qipa ↑} quantitative eval\\
		%\newline
		%\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		%\columnbreak

@@

		\headerbox{Morphotactics}{name=morphotactics,column=1,below=example}{
			\begin{itemize}
				\item Introduction of quasi-derivational verbal morphotactics
			\end{itemize}
			\centering
			\includegraphics[width=0.9\textwidth]{img/dibuix}

		\headerbox{Ongoing and future work}{name=nedostatki,column=1,below=morphotactics}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item \textbf{Kyrgyz} \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item \textbf{Tatar} \& \textbf{Bashkort} \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item \textbf{Kazakh} \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item \textbf{Kumyk} \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

@@

		\htwo{Treebanks}
		\vspace{-1em}
		\newline
			\tikzoverlay[text width=0.9\textwidth] at (0.55in, -0.5in) {
				\includegraphics[width=0.95\textwidth]{img/dep-graph}
			};
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{fmtjnw2015kazdep}
		\end{itemize}
		\includegraphics[width=0.63\textwidth]{img/korp}
		\begin{itemize}
			\item work on \textbf{Tuvan} ongoing
		\end{itemize}
		\vspace{1.45in}
		\dividerspace{}

@@

				%\item Current annotation of a dependency treebank for Kazakh:\\
				%a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%%\item Leading to
				%\begin{itemize}
				%	\item Improved rule-based morphological disambiguation% (constraint grammar)
				%	\item Improved morphological analyser %for Kazakh
				%	\item A syntactic dependency treebank %for Kazakh
				%\end{itemize}
				%%\item Work on rule-based morphological disambiguation with constraint grammar
			%\end{itemize}
			\htwo{Future work}
				\begin{itemize}
					%\item Annotate more gold standard text in more Turkic languages
					%\item Research cross-linguistic techniques for analysing Turkic
					\item Dependency parsing (native and crosslingual)
					\item Increase number of stems
					\item Make more available to linguists
					\item Integrate into end-user applications (spellchecking, MT)
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
		}

		\headerbox{Further information}{name=getting,column=0,below=development,span=3}{
			\tikzoverlay[text height=1in] at (0in, 0.04in) {
				\includegraphics[angle=90,height=1in]{apertium5b}
			};
			%\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
			\tikzoverlay[text height=1in] at (10in, 0.04in) {
				\includegraphics[height=1in]{qrcode}
			};
			\tikzoverlay[text height=0.5in] at (6.75in, 0.04in) {
				\parbox{3in}{
				\centering
				{\huge \textbf{Четтирдивис!}}\\
				\texttt{четтир\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{pl}}\vspace{1em}\\
				{\Large \url{http://turkic.apertium.org/}}
				}
			};
			\tikzoverlay[text width=6in] at (1in, 0.04in) {
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} on our website: \url{http://turkic.apertium.org/} %\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				\item \textbf{Source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
			};
			\vspace{1in}
		}

@@

>>>>

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\tiny}
\renewcommand*{\intitlepunct}{\space}

@@

	%\headerbox{Lexicon}{name=lexicon,column=1,below=example}{
	%	%\resizebox{0.9\textwidth}{!}{
	%	%}
	%}
		\headerbox{Morphotactics}{name=morphotactics,column=2,below=example}{
			\begin{itemize}
				\item Introduction of quasi-derivational verbal morphotactics
				\item Combinatorics not previously documented
			\end{itemize}
			\centering
			\includegraphics[width=0.9\textwidth]{img/dibuix}

		}
	\headerbox{Evaluation}{name=results,column=2,below=morphotactics}{ %lexicon}{
		%\begin{multicols}{2}	
		\htwo{5-part corpus for naïve coverage}
		%\begin{itemize}
		%	\item Naïve coverage calculated on 5-part corpus
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			 \textbf{Domain} & \textbf{Tokens} & \textbf{Coverage} (\%) \\
			\midrule
			 News       & 1,539,459 &  95.73  \\
			 Religion   & 746,124 &  93.84 \\
			 Literature & 297,830 &  91.96  \\
			 Encyclopaedic  & 276,547 & 90.86 \\
			 Folklore & 27,902 & 91.57  \\\cline{2-3}
			 Average    & -- & 92.79 \\
			\bottomrule
		\end{tabular}}
		\end{center}

		\htwo{Precision and recall}
		%\begin{itemize}
		%	\item Good results reflect high accuracy
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{llrr}
			\toprule
				& \textbf{count} & \textbf{precision} & \textbf{recall} \\
			\midrule
			known tokens & 1024 & 0.99 & 0.97 \\
			all tokens & 1425 & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}}
		\end{center}
		%{\qipa ↑} quantitative eval\\
		%\newline
		%\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		%\columnbreak

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=1,below=example}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item \textbf{Kyrgyz} \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item \textbf{Tatar} \& \textbf{Bashkort} \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item \textbf{Kazakh} \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item \textbf{Kumyk} \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

@@

		\htwo{Treebanks}
		\vspace{-1em}
		\newline
			\tikzoverlay[text width=0.9\textwidth] at (0.55in, -0.5in) {
				\includegraphics[width=0.95\textwidth]{img/dep-graph}
			};
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{fmtjnw2015kazdep}
		\end{itemize}
		\includegraphics[width=0.63\textwidth]{img/korp-2}
		\begin{itemize}
			\item work on \textbf{Tuvan} ongoing
		\end{itemize}
		\vspace{1.45in}
		\dividerspace{}

@@

				%\item Current annotation of a dependency treebank for Kazakh:\\
				%a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%%\item Leading to
				%\begin{itemize}
				%	\item Improved rule-based morphological disambiguation% (constraint grammar)
				%	\item Improved morphological analyser %for Kazakh
				%	\item A syntactic dependency treebank %for Kazakh
				%\end{itemize}
				%%\item Work on rule-based morphological disambiguation with constraint grammar
			%\end{itemize}
			\htwo{Future work}
				\begin{itemize}
					%\item Annotate more gold standard text in more Turkic languages
					%\item Research cross-linguistic techniques for analysing Turkic
					\item Dependency parsing (native and crosslingual)
					\item Increase number of stems
					\item Make more available to linguists
					\item Integrate into end-user applications (spellchecking, MT)
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
				\includegraphics[width=\textwidth]{img/tyv-spelling}
		}

@@

		\headerbox{Further information}{name=getting,column=0,below=references,span=3}{
			\tikzoverlay[text height=1in] at (0in, 0.04in) {
				\includegraphics[angle=90,height=1in]{apertium5b}
			};
			%\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
			\tikzoverlay[text height=1in] at (10in, 0.04in) {
				\includegraphics[height=1in]{qrcode}
			};
			\tikzoverlay[text height=0.5in] at (6.75in, 0in) {
				\parbox{3in}{
				\centering
				{\huge \textbf{Четтирдивис!}}\\
				\texttt{четтир\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{pl}}\vspace{1em}\\
				{\Large \url{http://turkic.apertium.org/}}
				}
			};
			\tikzoverlay[text width=6in] at (1in, 0.04in) {
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} on our website: \url{http://turkic.apertium.org/} %\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				\item \textbf{Source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
			};
			\vspace{1in}
		}
